### 2018-10-09 notes/glossary/glossary.tex
tmp commit

@@

>>>>

\newglossaryentry{ldg}{
	name=Linkage disquilibrium,
	text=linkage disquilibrium,
	description={Correlation between nearby variants such that the alleles at neighbouring markers (on the same chromosome) are associated within a population more often than if they were unlinked}
}

\newglossaryentry{heritability}{
	name=Heritability,
	text=heritability,
	description={The proportion of the variation in a given characteristic or state that can be attributed to (additive) genetic factors}
}

@@

\newglossaryentry{ld}{type=\acronymtype,name={LD},first={Linkage Disequilibrium (LD)\glsadd{ldg}},description={Linkage disquilibrium},see=[Glossary:]{ldg}}

### 2018-10-09 notes/notebook.tex
tmp commit

% My master tips book
\documentclass[a4paper, 12pt] {report}

% All of the packages imported for this document:
% \usepackage[utf8]{inputenc}
% \usepackage{glossaries}
% \usepackage{hyperref}
% \usepackage{setspace}
% \usepackage{url}
% \usepackage{multicol}

% Preamble:
\usepackage[T1]{fontenc}                                 % package for specifying output font encoding
\usepackage[acronym,style=super,nogroupskip,section=chapter]{glossaries} % package for making glossaries
\usepackage[flushleft]{threeparttablex}                  % package to add notes at the bottom of the table
\usepackage[font=footnotesize,format=hang]{caption}      % package for formatting figure caption
\usepackage[hidelinks, colorlinks]{hyperref}             % package for hyperlinking references - hidelinks option removes the ugly boxes around the huperlinks
\usepackage[md]{titlesec}                                % package for tweaking the chapter/section/subsection titles format
\usepackage[noabbrev,capitalise]{cleveref}               % package for referencing multiple referencing in a single \ref command
\usepackage[toc]{appendix}                               % package for making appendices
\usepackage[utf8]{inputenc}                              % package for specifying input font encoding
\usepackage{chngcntr}                                    % package for making continuous figure numbering, instead of section-based numbering
\usepackage{graphicx}                                    % package for graphics handling (i.e. figure images)
\usepackage{mathptmx}                                    % package for Times New Roman font
\usepackage{natbib}                                      % package for reference management
\usepackage{setspace}                                    % package for setting line space (used in title page)
\usepackage{xcolor,colortbl}                             % package for making colours
\usepackage{booktabs}                                    % package for better looking tables
\usepackage{longtable}                                   % package for tables that span multiple pages
\usepackage{siunitx}                                     % package for scientific notations and units
\usepackage{etoolbox}                                    % package to 'robustify' \bfseries
\usepackage{enumitem}                                    % package for tweaking lists

@@

\def\labelitemi{--}

\makeglossaries

@@

\include{./title/title}
\include{./glossary/glossary}

@@

\printglossaries
\clearpage

\include{./subnotes/intro}

@@

\bibliographystyle{BiocRefStyle}

>>>>

\documentclass[a4paper, 12pt, oneside]{report} % for final draft compilation
% \documentclass[a4paper, 12pt, oneside, draft]{report} % for draft compilation

% Preamble:
\usepackage[T1]{fontenc}                                 % package for specifying output font encoding
\usepackage[acronym,style=super,nogroupskip]{glossaries} % package for making glossaries
\usepackage[flushleft]{threeparttablex}                  % package to add notes at the bottom of the table
\usepackage[font=footnotesize,format=hang]{caption}      % package for formatting figure caption
\usepackage[hidelinks, colorlinks]{hyperref}             % package for hyperlinking references - hidelinks option removes the ugly boxes around the huperlinks
\usepackage[md]{titlesec}                                % package for tweaking the chapter/section/subsection titles format
\usepackage[noabbrev,capitalise]{cleveref}               % package for referencing multiple referencing in a single \ref command
\usepackage[toc]{appendix}                               % package for making appendices
\usepackage[utf8]{inputenc}                              % package for specifying input font encoding
\usepackage{chngcntr}                                    % package for making continuous figure numbering, instead of section-based numbering
\usepackage{graphicx}                                    % package for graphics handling (i.e. figure images)
\usepackage{mathptmx}                                    % package for Times New Roman font
\usepackage{natbib}                                      % package for reference management
\usepackage{setspace}                                    % package for setting line space (used in title page)
\usepackage{xcolor,colortbl}                             % package for making colours
\usepackage{booktabs}                                    % package for better looking tables
\usepackage{longtable}                                   % package for tables that span multiple pages
\usepackage{siunitx}                                     % package for scientific notations and units
\usepackage{etoolbox}                                    % package to 'robustify' \bfseries
\usepackage{enumitem}                                    % package for tweaking lists

% Define colour(s) for table rows:
\definecolor{LightCyan}{rgb}{0.88,1,1}

% Change the itemize bullet points to dash:
\def\labelitemi{--}

@@

% Change the default cref name for equations:
\creflabelformat{equation}{#2\textup{#1}#3}

% Change the default cref name for appendix:
\crefname{appcha}{Appendix}{Appendices}
\crefname{appsec}{Appendix}{Appendices}

% Make siunitx detect bold/italics/etc:
\robustify\bfseries
\sisetup{detect-all}

% Set the width of captions for threeparttable to \linewidth:
\captionsetup[threeparttable]{width=\linewidth}

% Set up continuous figures:
\DeclareCaptionFormat{cont}{#1 (cont.)\par}

% Change the default url font:
\urlstyle{rm}

% change figure numbering from section-based to continuous:
\counterwithout{figure}{chapter}
\counterwithout{equation}{chapter}
\counterwithout{table}{chapter}

% Change the title of bibliography to references:
\renewcommand{\bibname}{References}

% Change the title of Table of Contents:
\renewcommand{\contentsname}{Table of Contents}

% Change the title of Table of Contents:
% \renewcommand{\thesubfigure}{\Alph{subfigure}}

% Italicise the subsubsection title:
\titleformat{\subsubsection}{\normalfont\itshape\bfseries}{\thesubsubsection}{1em}{}
\titleformat{\paragraph}{\normalfont\itshape}{\theparagraph}{\noindent}{}

% Remove unnecessary spaces between the figures from different chapters in LoF and LoT:
\newcommand*{\noaddvspace}{\renewcommand*{\addvspace}[1]{}}
\addtocontents{lof}{\protect\noaddvspace}
\addtocontents{lot}{\protect\noaddvspace}

% For generating glossaries:
\include{./glossary/glossary}
\makeglossaries

% Specify graphics path:
\graphicspath{{./images/}}
\DeclareGraphicsExtensions{.pdf,.png,.jpg}

% Define some alias for very long citations:
% \defcitealias{TCGA}{NCI and NHGRI, 2016}
% \defcitealias{ICGC}{ICGC, 2016}
% \defcitealias{GEO}{NCBI, 2016}

@@

\include{./title/title}

\pagenumbering{roman} % set page numbering to roman numeral

\include{./subnotes/preface}

\addcontentsline{toc}{section}{Preface}

% \include{./misc/acknowledgement}

\addcontentsline{toc}{section}{\contentsname}

@@

\clearpage

% \addcontentsline{toc}{section}{\listfigurename}

% \listoffigures

% \clearpage

% \addcontentsline{toc}{section}{\listtablename}

% \listoftables

% \clearpage

\addcontentsline{toc}{section}{Glossary}

\printglossary[style=super]

% Need to set line spacing to single space, otherwise it inserts a blank page for an unknown reason:
% \singlespacing

\clearpage

\addcontentsline{toc}{section}{Acronyms}

\printglossary[type=\acronymtype,style=super]

\clearpage

\pagenumbering{arabic} % revert the page numbering to normal numbering
\glsresetall

@@

% \include{./methods/methods}

% \include{./results/results}

% \include{./results/results2}

% \include{./discussion/discussion}

% \include{./misc/appendix}

% \include{./misc/appendix2}

% Use the reference style specified in BiocRefStyle.bst:
\bibliographystyle{BiocRefStyle}

### 2018-10-09 notes/subnotes/gwas.tex
tmp commit

>>>>

\section{\glsdesc{ld}}
\label{sec:ld}

Consider two alleles or gene loci, A and B, that are on the same chromosome.
If these alleles are ``dependent'', then A and B will always segregate together.
Mathematically, the probability of both A and B segregating together is $P(AB)$.
Now, if A and B are ``independent'', then A being passed on to the offspring has no influence on B being passed on, and vice versa.
Mathematically, the probability of both A and B segregating in this case is given by $P(A)P(B)$.

\Gls{ld}, by definition, is the correlation between nearby variants such that the alleles at neighbouring markers on the same chromosome are associated within a population more often than they were unlinked.
In other words, {\bfseries \gls{ld} is a measure of how likely two alleles or loci are passed on to the offspring together}.
Mathematically, this is represented as:
\begin{equation}
	\label{eq:ld}
D = P(AB) - P(A)P(B)
\end{equation}
where $D$ is the coefficient of \gls{ld}.
When $D = 0$, A and B are said to be in equilibrium and will not segregate together.
On the other hand, when $D = 1$, A and B are said to be in perfect \gls{ld}, where A and B will always segregate together.

By measuring the \gls{ld} of two alleles, or in our case two markers, you are able to determine whether those alleles will be passed on together.
This means that only one marker is required to detect or track both alleles, if they are in strong \gls{ld}.
Therefore, you can choose several markers that represent several alleles that are in high \gls{ld} with the marker.
Furthermore, if that marker is associated with a disease, it is likely that at least one of the markers that are in high \gls{ld} with that marker is also associated with the disease.
This allows us to use less markers without losing any power to detect variants that are associated with the disease.
